### 2024-09-01 player-evaluation.qmd
20240901 - contract hold-outs

In addition to [injuries](#sec-evalHealth), other factors can affect a player's availability, including league suspensions, for instance, due to violating the league's conduct policy.

>>>>

In addition to [injuries](#sec-evalHealth), other factors can affect a player's availability, including contract hold-outs or league suspensions, for instance, due to violating the league's conduct policy.
Some players may be "holding out", which means that they may refuse to play until they sign a more desirable contract with the team (e.g., for more money or for a longer-term contract).
